A robust framework for variable extrusion width concentric toolpath generation

### 2019-08-05 12_conclusions_future_work.tex
rewrite skeletonization section and rename Voronoi Quadrangulation > Skeletal Trapezoidation
mention optimization of beading strategy in future work

\subsection{Future work}
Use Voronoi Quadrangulation to generate quad dominant meshings for FEM.

>>>>

\subsection{Future work}
Define the optimal strategy for a given piece of hardware by finding an accurate objective function which takes into account the manufacturability or dimensional accuracy as a function of bead width and its effect on qualities of top layers, stiffness or the dimensional accuracy of the outline shape.

Use Skeletal Trapezoidation to generate quad dominant meshings for FEM.
